Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-07-02 manuscript/manuscript.Rmd
Add comment on distribution.

out <- .plot_penguin_body_mass(plot_theme = plot_theme)
out$plot
```

>>>>

out <- .plot_penguin_body_mass(plot_theme = plot_theme)
out$plot
```
Shift- and scale-invariant transformation leads to a lower overall residual sum, indicating a better transformation.
Moreover, conventional transformations led to low standard deviation $\sigma_{YJ}$ of the body mass variable after transformation.
The empirical central normality test did not detect any statistically significant deviations from central normality for any transformation (all $p \geq 0.38$).
The distribution of the original data was not centrally normal ($p = 0.03$).
